test_for_p.values

### 2017-12-09 test4pvalues.Rmd

@@

```{r}
twenty <- AP_mouse_table[AP_mouse_table$Ncells > 20,]
lessTwenty <- AP_mouse_table[AP_mouse_table$Ncells < 20,]
#these will give the list of mice

@@

@@

@@

cat_list <- split(pMLH1_data, (pMLH1_data$mouse))
#list of dfs, that are split by mouse
#cat_list$'4jan17_LEW_f3'$quality  AND  cat_list[[1]]$quality
#cat_list[1]$quality

#remove sections which are in category but have no data
cat_list <- cat_list[ -c(7, 12, 14,19, 20) ]
#7: PERC male, 12:CAST female, 14:HMI female, 19:SPIC male

>>>>

```{r}
#setwd("C:/Users/alpeterson7/Documents/MLH1repo")
#setwd("Documents/MLH1repo")
setwd("C:/Users/April/Desktop/MLH1repo")
load(file="MLH1_data_setup.RData")
library(ggplot2)
```

@@

```{r}
twenty <- AP_mouse_table[AP_mouse_table$Ncells >= 20,]
lessTwenty <- AP_mouse_table[AP_mouse_table$Ncells < 20,]
#these will give the list of mice

@@

twenty_data <- MLH1_data[(unique(MLH1_data$mouse) %in% twenty$mouse),]
lessTwenty_data <- MLH1_data[(unique(MLH1_data$mouse) %in% lessTwenty$mouse),]

@@

```{r}

outlist = list()
for(o in 1:length(unique(twenty$mouse))){
  print(twenty$mouse[o])
  mus_data <- twenty_data[twenty_data$mouse == twenty$mouse[o],]

  outlist[o] <- list(replicate(100, t.test(sample(mus_data$adj_nMLH1.foci, 15, replace = TRUE),
                        sample(mus_data$adj_nMLH1.foci, 15, replace = TRUE) )$p.value ) )
  }
names(outlist) <- twenty$mouse
#outlist is not a list of p-value list. ()

#find a way to print out histogrms 
plot_list = list()
for (i in 1:length(twenty$mouse)){
  print(i)  
  try_df <- as.data.frame(outlist[[i]])
  colnames(try_df) <- "pvals"
  p = ggplot(try_df) +
        geom_histogram(aes(x=pvals) )#xlim
    plot_list[[i]] = p
}

# Save plots to tiff. Makes a separate file for each plot.
for(i in 1:length(plot_list) ) {
    file_name = paste("histy_", i, ".tiff", sep="")
    tiff(file_name)
    print(plot_list[[i]])
    dev.off()
}

hist(outlist[[5]])
plot()

@@

cat_list <- split(pMLH1_data, (pMLH1_data$mouse))
#list of dfs, that are split by mouse
#cat_list$'4jan17_LEW_f3'$quality  AND  cat_list[[1]]$quality
#cat_list[1]$quality
#remove sections which are in category but have no data
